CF Registry Analysis

### 2022-12-27 Christine Chan/CF Registry/cf_registry_analysis.qmd
a1c screening

>>>>

```{r}
#| label: tbl-screening_a1c
#| tbl-cap: "Yearly Screening Rates"
year_screen = function(df=encounter,year){
  # Filter and count
  inc = df %>% 
    filter(reviewyear==year,first_cfrd_both >= year) %>%
    mutate(hba1c = !is.na(hgba1c)) %>%
    group_by(eDWID) %>%
    summarise(hba1c = max(hba1c),`Age Group` = `Age Group`[1])
  inc = inc %>% group_by(hba1c) %>% count(`Age Group`) %>% filter(`Age Group` != "< 10")
  # Calculations
  total_screened = sum(inc$n[inc$hba1c==1])
  total_seen = sum(inc$n)
  screen_rate = total_screened/total_seen * 100

  screened_10_18 = inc$n[inc$hba1c==1 & inc$`Age Group` == "10 - 18"]
  seen_10_18 = sum(inc$n[inc$`Age Group` == "10 - 18"])
  rate_10_18 = screened_10_18/seen_10_18 *100

  screened_19_30 = inc$n[inc$hba1c==1 & inc$`Age Group` == "19 - 30"]
  seen_19_30 = sum(inc$n[inc$`Age Group` == "19 - 30"])
  rate_19_30 = screened_19_30/seen_19_30 *100

  screened_30 = inc$n[inc$hba1c==1 & inc$`Age Group` == "> 30"]
  seen_30 = sum(inc$n[inc$`Age Group` == "> 30"])
  rate_30 = screened_30/seen_30 *100

In @tbl-screening_a1c, people with CFRD (by either registry definition or OGTT) and those under 10 were excluded. Screening rate is calculated as the number of people with an HbA1c value divided by the total number of people seen in clinic that year.
